---
title: "Curriculum vitae"
description: |
  This page is still under construction.  
  You can download the pdf version [here](cv.pdf).
---



<link rel="stylesheet" href="assets/cv-styles.css">

```{r setup, include = FALSE}
library(tidyverse)
library(bibtex)
library(lubridate)
library(knitr)
library(kableExtra)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
knit_pdf <- FALSE
```

<!--
Needs to be knitted twice for pdf to be updated to the latest.
-->


<main class="cv-canvas">

# [E]{.bigger}MI [T]{.bigger}ANAKA

<i class="fas fa-envelope"></i> emi.tanaka@monash.edu
<i class="fab fa-twitter"></i> @statsgen
<i class="fab fa-github"></i> emitanaka
<i class="fas fa-globe"></i> emitanaka.org


### skill stack

::: half

R, HTML/CSS, LaTeX, Git/GitHub

:::

### research interests

::: half

experimental design, mixed models, statistical graphics, bioinformatics, statistical genetics

:::

## employment

```{r}
small <- function(x) paste0("<div style='font-size:0.75rem;line-height:0.9rem;'>", x, "</div>")
dat <- read_csv("__cvdata/employment.csv") %>% 
  mutate(start = dmy(start),
         end = dmy(end))
dat %>% 
  mutate(start = sprintf("%d/%.2d", year(start), month(start)),
         end = sprintf("%d/%.2d", year(end), month(end)),
         end = ifelse(end=="NA/NA", "current", end),
         date = small(paste0(start, "-", end)),
         org = small(paste0(org, ", ", suborg))) %>% 
  select(date, position, org) %>% 
  kable(col.names = c("", "", ""), escape = FALSE,
        align = "llr")
```

## education

**PhD, Statistics**  
Statistical Methods for Improving Motif Evaluation  
Supervisor: Dr. Uri Keich  
School of Mathematics and Statistics  
The University of Sydney  
2015 | Sydney, Australia  

**BSci (Adv Maths), Honour I**  
Major in Mathematics and Statistics  
The University of Sydney  
2010 | Sydney, Australia  

## publications

```{r, results="asis"}
res <- read.bib("__cvdata/pubs.bib")
res[names(res)!="Tanaka2015-od"] # remove thesis
```


## presentations


## workshops

## awards & distinctions

```{r}
dat <- read_csv("__cvdata/awards.csv")
dat %>% 
  mutate(main = paste(name, small(significance)),
         money = scales::dollar(money),
         money = ifelse(is.na(money), "", money)) %>% 
  select(award_year, main, money) %>% 
  kable(col.names = c("", "", ""), escape = FALSE) %>% 
  column_spec(2, width = "30em") %>% 
  column_spec(c(1, 3), extra_css = "vertical-align: top;")
```


</main>

```{r, eval=knit_pdf}
pagedown::chrome_print(input = "docs/cv.html",
                       output = "cv.pdf")
```

