---
title: "Curriculum vitae"
description: |
  This page is still under construction.  
  You can download the pdf version [here](cv.pdf).
---



<link rel="stylesheet" href="assets/cv-styles.css">

```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(glue)
library(kableExtra)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
knit_pdf <- TRUE

small <- function(x) paste0("<div style='font-size:0.75rem;line-height:0.9rem;'>", x, "</div>")
```

<!--
Needs to be knitted twice for pdf to be updated to the latest.
-->


<main class="cv-canvas">

# [E]{.bigger}MI [T]{.bigger}ANAKA

<i class="fas fa-envelope"></i> emi.tanaka@monash.edu
<i class="fab fa-twitter"></i> @statsgen
<i class="fab fa-github"></i> emitanaka
<i class="fas fa-globe"></i> emitanaka.org


### skill stack

::: half

R, HTML/CSS, LaTeX, Git/GitHub

:::

### research interests

::: half

experimental design, mixed models, statistical graphics, bioinformatics, statistical genetics

:::

## employment

```{r work}
work <- read_csv("../cv/data/employment.csv") %>% 
  mutate(start = dmy(start),
         end = dmy(end))
work %>% 
  mutate(start = sprintf("%d/%.2d", year(start), month(start)),
         end = sprintf("%d/%.2d", year(end), month(end)),
         end = ifelse(end=="NA/NA", "current", end),
         date = small(paste0(start, "-", end)),
         org = small(paste0(org, ", ", suborg))) %>% 
  select(date, position, org) %>% 
  kable(col.names = c("", "", ""), escape = FALSE,
        align = "llr")
```

## education

**PhD, Statistics**  
Statistical Methods for Improving Motif Evaluation  
Supervisor: Dr. Uri Keich  
School of Mathematics and Statistics  
The University of Sydney  
2015 | Sydney, Australia  

**BSci (Adv Maths), Honour I**  
Major in Mathematics and Statistics  
The University of Sydney  
2010 | Sydney, Australia  

## publications

<ol>
```{r pubs, results='asis'}
pubs_key <- read_csv("../cv/data/pubs-key.csv") %>% 
  separate_rows(pubid, sep = ", ")
scholar <- scholar::get_publications("v8FN0qoAAAAJ") %>% 
  select(pubid, cites, year) %>% 
  right_join(pubs_key, by = "pubid") %>% 
  group_by(id) %>% 
  summarise(citations = sum(cites),
            year = max(year))
pubs <- vitae::bibliography_entries("../cv/data/pubs.bib") %>% 
  left_join(scholar, by = "id") %>% 
  as_tibble() %>% 
  arrange(desc(issued))

pubs %>% 
  mutate(author = map(author, ~map_chr(.x, function(x) {
            if(x$family=="Tanaka" & x$given=="Emi") {
              glue("<b>{x$family}, {substr(x$given, 1, 1)}</b>")
            } else {
              glue("{x$family}, {substr(x$given, 1, 1)}")
            } 
          })),
         author = map_chr(author, ~knitr::combine_words(.x, and = " & ")),
         journal = ifelse(is.na(`container-title`), "PhD Thesis", `container-title`)) %>% 
  mutate(text = glue("{author} ({year}) {title}. <i>{journal}</i>"),
         text = case_when(!is.na(volume) & !is.na(issue) ~ glue("{text}, {volume}({issue})"),
                          !is.na(volume) ~ glue("{text}, {volume}"),
                          TRUE ~ text),
         text = ifelse(!is.na(page), glue("{text}, {page}"), text),
         text = ifelse(citations > 0, glue("{text}. <i>Citations: <b>{citations}</b></i>."), text)) %>% 
  pull(text) %>% 
  paste0("<li>", ., "</li>") %>% 
  cat()
```
</ol>

<span style="font-size:0.7rem">Citation counts are sourced from Google Scholar at `r today()`.</span>

## talks

(Note: work-in-progress - data incomplete)

<span style="font-size:0.7rem">
List of talks (and links to the slides if available) are at <b>https://emitanaka.org/talks.html</b>.  
Below show the last 10 talks.
</span>

```{r talk}
read_csv("../cv/data/talks.csv") %>% 
  mutate(date = dmy(date)) %>% 
  slice_max(order_by = date, n = 10) %>% 
  select(date, title, host) %>% 
  mutate(date = small(date),
         host = small(host)) %>% 
  kable(col.names = c("", "", ""), escape = FALSE) %>% 
  column_spec(2, width = "25em") %>% 
  column_spec(c(1, 3), extra_css = "vertical-align: top;")
```


## workshops

(Note: work-in-progress -  data incomplete)

```{r workshop}
read_csv("../cv/data/workshops.csv") %>% 
  filter(parent!="no") %>% 
  mutate(date = dmy(date_start),
         date = small(glue("{year(date)}/{month(date)}")),
         text = title,
         text = ifelse(is.na(copresenters), 
                       text, 
                       paste0(text, small(glue("<i>Co-presented with {copresenters}.</i>")))),
         text = ifelse(is.na(host), 
                       text, 
                       paste0(text, small(glue("<i>Hosted by {host}.</i>"))))) %>% 
  select(date, text) %>% 
  kable(col.names = c("", ""), escape = FALSE) %>% 
  column_spec(c(1, 2), extra_css = "vertical-align: top;")
```


## service

```{r service}
service <- read_csv("../cv/data/service.csv")
service %>% 
  mutate(end = ifelse(is.na(end), "ongoing", end),
         date = small(paste0(start, "-", end)),
         org = paste0(org, ", ", suborg)) %>% 
  select(date, org, position) %>% 
  kable(col.names = c("", "", ""), escape = FALSE) %>% 
  column_spec(c(1, 2, 3), extra_css = "vertical-align: top;")
```

## professional memberships

* Statistical Society of Australia 
* International Biometrics Society

## awards & distinctions

```{r}
awards <- read_csv("../cv/data/awards.csv") 
awards %>% 
  mutate(significance = replace_na(significance, ""),
         main = name,
         main = ifelse(is.na(lead), main, paste(main, small(paste("Lead:", lead)))),
         main = paste(main, small(significance)),
         money = scales::dollar(money),
         money = replace_na(money, "")) %>% 
  select(award_year, main, money) %>% 
  kable(col.names = c("", "", ""), escape = FALSE) %>% 
  column_spec(2, width = "30em") %>% 
  column_spec(c(1, 3), extra_css = "vertical-align: top;")
```


</main>

```{r, eval=knit_pdf}
pagedown::chrome_print(input = "docs/cv.html",
                       output = "cv.pdf")
```

